---
title: "Question 2- Plotly set up"
output: 
  html_document:
    toc: true
    toc_float: true
---
Looking at Instacart data. 
```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
library(stringr)
```

To stratify the large data set, we will only be looking at data about Organic produce that was bought on Sunday(1), and was a first time order. 
```{r}
data("instacart")

instacart_df = 
  instacart %>%
  na.omit(instacart) %>% #omitting any NA
  select(order_id, add_to_cart_order, reordered, user_id, order_dow, order_hour_of_day, product_name, department) %>% #Selecting variables
  filter(str_detect(product_name, "Organic"), # Only organic items are shown
         reordered == "0", order_dow == "1", #Only 1st time orders that were ordered on Sunday(1) are shown. 
         department %in% c("produce")) %>% # Remove any orders in departments that do not include edible items
  mutate(product_name = str_replace_all(product_name, 
                                        c("Organic Bluberries" = "Organic Blueberries", 
                                          "Organic Blueberry" = "Organic Blueberries"))) #There were multiple names for blueberries

unique(instacart_df$department)
```

# Plotly plots
## Scatterplot
```{r}
#Set up data for scatterplot
produce_1to5 <- instacart_df %>% 
  group_by(product_name) %>%   # Group by product name
  summarize(
    total_count = n(),    # Count total purchases of each product
    order_count = sum(add_to_cart_order %in% 1:5) # % where that was one of the 1st five products they put in their cart
  ) %>%
    filter(total_count > 1) %>% #Removed foods where there was only 0 or 1 bought because it was messing with the graph
  mutate(order_percent = (order_count / total_count) * 100) # Calculate percentage for the amount of orders


produce_1to5 %>%
  mutate(text_label = str_c("Product Name:", product_name)) %>%
  plot_ly(x = ~total_count, y = ~order_percent, color = ~product_name, type = "scatter", mode = "markers", colors = "viridis") #when the legend is on there, it only shows the legend in website, not the graph itself
```
This scatterplot shows the percentage of each Organic produce item that was one of the first five items to be put in the user's cart on a Sunday, not including any reorders. 
*Double press on item in the legend to isolate it. *

# Barplot
```{r}
instacart_df %>%
  count(product_name) %>%
  filter(str_detect(product_name, "berries|berry|Berries|Berry")) %>%
  mutate(product_name = fct_reorder(product_name, n)) %>%
  plot_ly( 
    x = ~product_name, y = ~n, 
    color = ~product_name, type = "bar", colors = "viridis")
```
The barplot shows the number of each Organic berry items that was bought on a Sunday, not including any reorders. 
*Double press on item in the legend to isolate it. *

# Boxplot
```{r}
instacart_df %>%
    filter(str_detect(product_name, "berries|berry|Berries|Berry")) %>%
  plot_ly( 
    x = ~product_name, y = ~order_hour_of_day, 
    color = ~product_name, type = "box", colors = "viridis")
```
The boxplot shows the time of day that the Organic berry items were bought on a Sunday, not including any reorders. 
*Double press on item in the legend to isolate it. *